---
title: "ANALYSIS REPORT"
author: "Master"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:  
    includes:
    code_folding: "hide"
    toc: true
    toc_float: false
    number_sections: false
  pdf_document:
    extra_dependencies: ["float"]
repro:
  data:
    data_Master_full: Enquete_Master.sav
    
  packages: [ aaronpeikert/repro@devel, crsh/papaja@devel, tinylabels, apaTables, haven, ggplot2,  tidyverse, gtsummary, car, GGally, MASS, matrixStats, rcompanion, moments, utils, sjPlot, interactions, kableExtra]
  scripts: clean.R
---

### Setup {-}

```{r setup , results='hide', message=FALSE, warning=FALSE}

library(repro)
# # load packages from yaml header
# automate_load_packages()
# # include external scripts
# automate_load_scripts()

# load data
data_Master_full   <- haven::read_sav("Enquete_Master.sav")

pacman::p_load(papaja, tinylabels, apaTables, haven, ggplot2,  tidyverse, gtsummary, car, GGally, MASS, matrixStats, rcompanion, moments, utils, sjPlot, interactions, kableExtra)

sessio = sessionInfo(); #opts_chunk$set(echo = F, message=F, warning=F) # set echo F for all

  
```

This file was automatically created via `the Repro package (version 0.1.0)` using  `r sessio$R.version$version.string`




```{r options, results='hide', message=FALSE, warning=FALSE}
options(scipen = 666, warn=-1, contrasts=c("contr.sum","contr.poly"), knitr.kable.NA = '')  #remove scientific notation # remove warnings #set contrasts to sum ! 
set.seed(666) #set random seed

# panderOptions('knitr.auto.asis', FALSE) #remove auto styling

# Look at R/clean.R (listed in the YAML) which does all the preprocessing for more info


# If you are unsure weather or not you have `git` `make` & `docker`.
# check_git()
# check_make()
# check_docker()
```




```{r clean, include=FALSE,  cache = TRUE}
path=here::here()
setwd(path)
source('./clean.R', echo=F)
# this chunk runs clean.R (listed in the YAML) which does all the preprocessing
```

### Introduction
Blabla

#### Demographics
```{r demographics}
base[c("Age", "Gender", "Profession")] %>%  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),)  %>% modify_caption("**Table 1. Demographics **") %>%
  bold_labels()

base[c("Decision Mode")] %>%  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),)   %>% modify_caption("**Table 2. Decision Mode **") %>%
  bold_labels()
```
$~$
$~$


```{r demographics_clean}
base_clean[c("Age", "Gender", "Profession")] %>%  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),)  %>% modify_caption("**Table 3. Demographics after cleaning**") %>%
  bold_labels()

base_clean[c("Decision Mode")] %>%  tbl_summary(statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),)   %>% modify_caption("**Table 4. Decision Mode after cleaning**") %>%
  bold_labels()
```
$~$
$~$

### Statistics

$~$
$~$



#### Price
```{r lm Price}
base_price = base_clean #no huge outliers, see appendix

final_price = lm(Price ~ Priming*Product*score + Age + Decision_mode,  data = base_price)

apa_lm <- apa_print(anova(final_price))
apa_table(apa_lm$table,  caption = "Anova table for Price.")
```

```{r, results="hide"}

plot_model(final_price)

interactions::cat_plot(final_price, pred = Priming, modx = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), modx.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Price Evaluation")   

interactions::interact_plot(final_price, pred = score, modx = Priming, interval = TRUE, plot.points = T, modx.labels = c("Computational","Affective"), point.alpha =0.3, x.label = "Affective Score towards climate change", y.label = "Price Evaluation")    


interactions::interact_plot(final_price, pred = score, modx = Priming, interval = TRUE, plot.points = F, modx.labels = c("Computational","Affective"), point.alpha =0.3, x.label = "Affective Score towards climate change", y.label = "Price Evaluation")    

```
$~$
$~$

Example for reporting :\

The priming condition (`r apa_lm$full_result$Priming`) and the affective score towards climate change (`r apa_lm$full_result$score`) did not affect price evaluation by themselves. However, the effect of affective score towards climate change on the price evalution slightly differed by priming condition, `r apa_lm$full_result$Priming_score`.

$~$

However it is important to note the very small effect size  `r "$\\hat{\\eta}^2_G = .014$"` and that the confidence intervals of the effect size includes 0  `r "90\\% CI $[.000, .044]$"` .
$~$ 

Grand biais vers 0 avec les positive affect scale. Resultat pas très interpretable donc... Mais je laisse les deux graphs au cas ou.

$~$
$~$




#### Probability to buy
```{r lm Buy}
base_buy = filter(base_clean, id %notin% c("13804")) #remove huge outliers, see appendix


final_buy = lm(Buy ~ Priming*Product*score + Age + Decision_mode,  data = base_buy)   

apa_lm <- apa_print(anova(final_buy))
apa_table(apa_lm$table,  caption = "Anova table for Probability to buy.")
```

```{r, results="hide"}
sjPlot::plot_model(final_buy)


interactions::cat_plot(final_buy, pred = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Probability to buy")   

sjPlot::plot_model(final_buy, type = "pred", show.data = T)[4]

interactions::cat_plot(final_buy, pred = Priming, modx = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), modx.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Probability to buy")   
```

$~$
$~$

#### Reccomendation
```{r lm Recco}
base_recco = base_clean #no huge outliers, see appendix

final_recco = lm(Reccomend ~ Priming*Product*score + Decision_mode + Age,  data = base_recco)
      

apa_lm <- apa_print(anova(final_recco))
apa_table(apa_lm$table,  caption = "Anova table for Reccomendation.")
```

```{r, results="hide"}

plot_model(final_recco)

interactions::cat_plot(final_recco, pred = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Reccomendation to buy")  

# sjPlot::plot_model(final_recco, type = "pred", show.data = T)[5]

interactions::cat_plot(final_recco, pred = Priming, modx = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), modx.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Reccomendation to buy")  

# interactions::interact_plot(final_recco, pred = negatif_affect, modx = Product, interval = TRUE, plot.points = T, point.alpha =0.3, modx.labels = c("A+","A++"), x.label = "Negative affect towards climate change", y.label = "Reccomendation to buy")  
# 
# interactions::interact_plot(final_recco, pred = negatif_affect, modx = Product, interval = TRUE, plot.points = F, point.alpha =0.3, modx.labels = c("A+","A++"), x.label = "Negative affect towards climate change", y.label = "Reccomendation to buy") 
```
$~$
$~$

<!-- negatif_affect barely significatif and doesn't look very informative by itself mais l'interaction mest plus interessante (avec et sans les points pour que ce soit plus digeste) -->

<!-- $~$ -->
<!-- $~$ -->
<!-- Example for reporting :\ -->

<!-- Product (`r apa_lm$full_result$Product`) and Negative affect towards climate change (`r apa_lm$full_result$negatif_affect`) affected reccomendation. However, the effect of Behav_enviro differed by Product, `r apa_lm$full_result$Product_negatif_affect`. -->



  
#### Ecologic Evaluation
  
  
```{r lm Ecolo_Eval}

base_eco = filter(base_clean, id %notin% c("13594", "11200", "13804", "12529", "11017")) #remove huge outliers, see appendix

final_eco = lm(Ecolo_Eval ~ Priming*Product*score  + Age + Decision_mode,  data = base_eco)

apa_lm <- apa_print(anova(final_eco))
apa_table(apa_lm$table, caption = "Anova table for Ecological evaluation")
```

```{r, results="hide"}

plot_model(final_eco)

interactions::cat_plot(final_eco, pred = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Ecological Evaluation") 

interactions::cat_plot(final_eco, pred = Priming, modx = Product, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), modx.labels = c("A+","A++"), errorbar.width = 0.4, y.label = "Ecological Evaluation") 

```


$~$
$~$

### Appendix

$~$
$~$

#### Score of Affect towards climate change
$~$
score = -negatif_affect 
$~$
score = score+positive_affect

$~$
$~$


#### Plot All



```{r plot all}
base_clean %>%
   keep(is.numeric) %>%
   ggpairs()
```
$~$
$~$

Check variables densities -> Positive and negative are not really good: to skewed. Score is quite better.¨

$~$
$~$

<!-- #### Price A++ -->
```{r lm PriceA+}
# base_priceA = dplyr::filter(base_price, Product == "A++")
# 
# final_priceA = lm(Price ~ Priming*Decision_mode + Age,  data = base_priceA)
# 
# apa_lm <- apa_print(anova(final_priceA))
# apa_table(apa_lm$table,  caption = "Anova table for Price with only A++ product.")
```

```{r, results="hide"}
# plot_model(final_priceA)
# 
# interactions::cat_plot(final_priceA, pred = Priming, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), errorbar.width = 0.4, y.label = "Price Evaluation")    
```

$~$
$~$

<!-- #### Probability to buy A++ -->
```{r lm BuyA}
# base_buyA = filter(base_buy, Product == "A++")
# 
# final_buyA = lm(Buy ~ Priming*Decision_mode + Age ,  data = base_buyA)
# 
# apa_lm <- apa_print(anova(final_buyA))
# apa_table(apa_lm$table,  caption = "Anova table for Probability to buy only A++ product.")
```


```{r, results="hide"}
# plot_model(final_buyA)
# 
# interactions::cat_plot(final_buyA, pred = Priming, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), errorbar.width = 0.4, y.label = "Probability to buy")   


```

$~$
$~$


<!-- #### Reccomendation A++ -->
```{r lm ReccoA}
# base_reccoA = filter(base_recco, Product == "A++")
# 
# final_reccoA = lm(Reccomend ~ Priming*Decision_mode + Age,  data = base_reccoA)
# 
# apa_lm <- apa_print(anova(final_reccoA))
# apa_table(apa_lm$table,  caption = "Anova table for Reccomendation to buy only A++ product.")
```

```{r, results="hide"}
# plot_model(final_reccoA)
# 
# interactions::cat_plot(final_reccoA, pred = Priming, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), errorbar.width = 0.4, y.label = "Reccomendation to buy") 
```

$~$
$~$

<!-- #### Ecologic Evaluation A++ -->
  
```{r lm Ecolo_EvalA+}
# base_ecoA = filter(base_eco, Product == "A++")
# 
# 
# final_ecoA = lm(Ecolo_Eval ~ Priming*Decision_mode  + Age,  data = base_ecoA)
# 
# apa_lm <- apa_print(anova(final_ecoA))
# apa_table(apa_lm$table, caption = "Anova table for Ecological evaluation only A++ product")
```


```{r, results="hide"}
# plot_model(final_ecoA)
# 
# interactions::cat_plot(final_ecoA, pred = Priming, interval = TRUE, plot.points = T, point.alpha =0.3, pred.labels = c("Computational","Affective"), errorbar.width = 0.4, y.label = "Price Evaluation")    
```
$~$
$~$


####  Correlation between affects towars climate change
```{r corr, echo=FALSE, message=FALSE, warning=FALSE}
base_clean$Gender = recode_factor(base_clean$Gender, "Autre/NA" = NA_character_)

ggpubr::ggscatter(base_clean, x = "negatif_affect", y = "positive_affect", position = position_jitter(w = 0.1, h = 0.1),
                  color = "black", shape = 21, size = 3, # Points color, shape and size
                  add = "reg.line",  # Add regressin line
                  add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
                  cor.coeff.args = list(method = "pearson", label.x = 6, label.sep = "\n")
)
```

$~$
$~$

#### Test frequencies between priming groups (Positive affect)
```{r glm, echo=FALSE, message=FALSE, warning=FALSE}

base_clean[c("positive_affect", "Priming")] %>%  tbl_summary(by=positive_affect)  %>% modify_caption("**Summary statistics**") %>% bold_labels() %>%
  add_p() %>% bold_labels()
```

$~$
$~$

#### Test frequencies between priming groups (Negative affect)
```{r frq, echo=FALSE, message=FALSE, warning=FALSE}

base_clean[c("negatif_affect", "Priming")] %>%  tbl_summary(by=negatif_affect)  %>% modify_caption("**Summary statistics**") %>% bold_labels() %>%
  add_p(test.args = "Priming" ~ list(workspace=2e9)) %>% bold_labels()
```

$~$
$~$

####  Logistic regression to predict priming groups (Positive affect)
```{r glm1, echo=FALSE, message=FALSE, warning=FALSE}

m1 <- glm(
    data = base_clean,
    Priming ~ positive_affect,
    family = binomial)

apa_lm <- apa_print(m1)
# Delete the "(Intercept)" line:
apa_lm$table <- apa_lm$table[-1, ]
apa_table(apa_lm$table)

p1 <- ggplot(base_clean, aes(x = positive_affect, y = as.numeric(as.character(Priming)))) +
    geom_point(colour = "red", alpha = 0.5) +
    stat_smooth(method = "glm", se = TRUE, method.args = list(family = binomial)) +
    labs(x = "Positive Affect", y = "Priming Probability", tag = "a") +
    theme_light() +
    theme(
        plot.tag = element_text(),
        axis.title = element_text(size = 7, face = "bold")
    )
```

$~$
$~$

```{r, fig.show="hold", out.width="50%", echo=FALSE, message=FALSE, warning=FALSE}
p1
```

$~$
$~$

####  Logistic regression to predict priming groups (Negative affect)
```{r glm2, echo=FALSE, message=FALSE, warning=FALSE}

m2 <- glm(
    data = base_clean,
    Priming ~ negatif_affect,
    family = binomial
  )

apa_lm <- apa_print(m2)
# Delete the "(Intercept)" line:
apa_lm$table <- apa_lm$table[-1, ]
apa_table(apa_lm$table)


p2 <- ggplot(base_clean, aes(x = negatif_affect, y = as.numeric(as.character(Priming)))) +
    geom_point(colour = "red", alpha = 0.5) +
    stat_smooth(method = "glm", se = TRUE, method.args = list(family = binomial)) +
    labs(x = "Negative Affect", y = "Priming Probability", tag = "a") +
    theme_light() +
    theme(
        plot.tag = element_text(),
        axis.title = element_text(size = 7, face = "bold")
    )

```

$~$
$~$

```{r, fig.show="hold", out.width="50%", echo=FALSE, message=FALSE, warning=FALSE}
p2
```
$~$
$~$

####  Logistic regression to predict priming groups (Affective Score)
```{r glm3, echo=FALSE, message=FALSE, warning=FALSE}

m3 <- glm(
    data = base_clean,
    Priming ~ score,
    family = binomial
  )

apa_lm <- apa_print(m3)
# Delete the "(Intercept)" line:
apa_lm$table <- apa_lm$table[-1, ]
apa_table(apa_lm$table)


p3 <- ggplot(base_clean, aes(x = score, y = as.numeric(as.character(Priming)))) +
    geom_point(colour = "red", alpha = 0.5) +
    stat_smooth(method = "glm", se = TRUE, method.args = list(family = binomial)) +
    labs(x = "Affective Score", y = "Priming Probability", tag = "a") +
    theme_light() +
    theme(
        plot.tag = element_text(),
        axis.title = element_text(size = 7, face = "bold")
    )

```

$~$
$~$

```{r, fig.show="hold", out.width="50%", echo=FALSE, message=FALSE, warning=FALSE}
p3
```
$~$
$~$
  
#### Visual check normality
  
```{r annexes, fig.show="hold", out.width="50%"}

plotNormalHistogram(base_clean$Price, main = "Price", sub = paste("skewness =", skewness(base_clean$Price, na.rm = TRUE))) 


# print("Check price density by product")
# densityPlot(base_clean$Price, g = base_clean$Product) # by product

plotNormalHistogram(base_clean$Reccomend, main = "Reccomendation", sub = paste("skewness =", round(skewness(base_clean$Reccomend, na.rm = TRUE)),2))



plotNormalHistogram(base_clean$Buy, main = "Probability to buy", sub = 
                      paste("skewness =", round(skewness(base_clean$Buy, na.rm = TRUE),2)))


plotNormalHistogram(base_clean$Ecolo_Eval, main = "Ecologic Evaluation", sub =
                      paste("skewness =", round(skewness(base_clean$Ecolo_Eval, na.rm = TRUE),2)))

```

$~$
$~$
  
  
#### Model selection for price
```{r diag lm MSprice, echo=FALSE, message=FALSE, warning=FALSE}
modprice = lm(Price ~ Priming*Product*negatif_affect + Priming*Product*positive_affect + Priming*Product*Decision_mode + Priming*Product*Age, data = base_clean)


MS = MASS::stepAIC(modprice, direction = "both", trace = FALSE)

x = kable(attributes(MS$anova)$heading, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(1, bold=T,align='c') 
gsub("<thead>.*</thead>", "", x)


kable(MS$anova, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0, bold=T,align='c')

```

$~$
$~$
  
#### Price: Diagnostics Plots for linear model 
  
```{r diag lm Price2, echo=FALSE, results='hide',  fig.show="hold", out.width="50%"}
modprice = lm(Price ~ Priming + Product  + Age + Priming:Product, data = base_price)

plot(modprice, c(1:2,4), labels.id = base_price$id)
sjPlot::plot_model(modprice, type="diag")[[3]]
```

$~$
$~$

#### Model selection for Probality to buy
```{r diag lm MSbuy, echo=FALSE, message=FALSE, warning=FALSE}

modbuy = lm(Buy ~ Priming*Product*negatif_affect + Priming*Product*positive_affect + Priming*Product*Decision_mode + Priming*Product*Age, data = base_clean)

MS = MASS::stepAIC(modbuy, direction = "both", trace = FALSE)

x = kable(attributes(MS$anova)$heading, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(1, bold=T,align='c') 
gsub("<thead>.*</thead>", "", x)


kable(MS$anova, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0, bold=T,align='c')

```

$~$
$~$
  
  
#### Probability to buy: Diagnostics Plots for linear model  
```{r diag lm Buy2, echo=FALSE, results="hide", fig.show="hold", out.width="50%"}
modbuy = lm(Buy ~ Product*Priming  + Age + Product:Behav_enviro, data = base_buy)

plot(modbuy, c(1:2,4), labels.id = base_buy$id)
sjPlot::plot_model(modbuy, type="diag")[[3]]
```

$~$
$~$
  
#### Model selection for Reccomendation
```{r diag lm MSrecco, echo=FALSE, message=FALSE, warning=FALSE}

modrecco = lm(Reccomend ~ Priming*Product*negatif_affect + Priming*Product*positive_affect + Priming*Product*Decision_mode + Priming*Product*Age, data = base_clean)

MS = MASS::stepAIC(modrecco, direction = "both", trace = FALSE)

x = kable(attributes(MS$anova)$heading, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(1, bold=T,align='c') 
gsub("<thead>.*</thead>", "", x)


kable(MS$anova, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0, bold=T,align='c')

```


$~$
$~$
  
#### Reccomendation: Diagnostics Plots for linear model AFTER
```{r diag lm Recco2, echo=FALSE, results="hide", fig.show="hold", out.width="50%"}
modrecco = lm(Reccomend ~ Priming*Product  + Product:Behav_enviro, data = base_recco)

plot(modrecco, c(1:2,4), labels.id = base_recco$id)
sjPlot::plot_model(modrecco, type="diag")[[3]]
```

$~$
$~$
  

#### Model selection for Ecologic Evaluation
```{r diag lm MSeco, echo=FALSE, message=FALSE, warning=FALSE}
modeco = lm(Ecolo_Eval ~ Priming*Product*negatif_affect + Priming*Product*positive_affect + Priming*Product*Decision_mode + Priming*Product*Age, data = base_clean)

MS = MASS::stepAIC(modeco, direction = "both", trace = FALSE)

x = kable(attributes(MS$anova)$heading, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(1, bold=T,align='c') 
gsub("<thead>.*</thead>", "", x)


kable(MS$anova, format="html") %>%
    kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%  row_spec(0, bold=T,align='c')

```

$~$
$~$
  
#### Ecologic Evaluation: Diagnostics Plots for linear model AFTER
```{r diag lm EcoEval, echo=FALSE, results="hide", fig.show="hold", out.width="50%"}
modeco = lm(Ecolo_Eval ~ Priming*Product*Decision_mode  + Priming*Product*Age, data = base_eco)

plot(modeco, c(1:2,4), labels.id = base_eco$id)
sjPlot::plot_model(modeco, type="diag")[[3]]
```

$~$
$~$
  
  
  
##### Hollistic (Positive) Affect Towards Climate Change


```{r}

plotNormalHistogram(base_clean$positive_affect, main = "Positive Affect", sub = paste("skewness =", skewness(base_clean$positive_affect, na.rm = TRUE))) 

```

$~$
$~$

We see a strong right skew of the dristribution.

$~$
$~$

##### Hollistic (Negative) Affect Towards Climate Change


```{r}

plotNormalHistogram(base_clean$negatif_affect, main = "Negative Affect", sub = paste("skewness =", skewness(base_clean$negatif_affect, na.rm = TRUE))) 

```

$~$
$~$

We see a slight left skew of the dristribution.

```{r}
report::report_packages()
```

